---
title: "case study"
author: "cathy"
date: "2024-10-08"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)
data(nyc_airbnb)
```


## Brainstorm questions

* Where are max and min air bnb prices?
 * What are average prices?
 * What factors affect prices?
* What are prices going up and down over time?
* What's the relationship between number of reviews and average rivew?
* Does room type affect availability?
* What's the location of the unit?
 * What areas are popular?
* Popularity = number of units? Average price?
* Are there repeat hosts?
 * If so, what does that mean?
 
Let's start coding

```{r}
max(pull(nyc_airbnb, price))
min(pull(nyc_airbnb, price))
mean(pull(nyc_airbnb, price))
```

```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

```{r}
plot = ggplot(data = nyc_airbnb, aes(x = room_type, y = availability_365)) +
  geom_violin()
print(plot)
```

```{r}
nyc_airbnb %>%
  ggplot(aes(x = neighbourhood_group, y = log(price))) +
  geom_boxplot()
```

```{r}
 nyc_airbnb |> 
   filter(
     neighbourhood_group == "Manhattan",
     price < 1000) |> 
   slice(1:10) |> 
   leaflet()|> 
   addTiles() |> 
   addMarkers(~lat, ~long)
```     

add color to the map
```{r}
 pal <- colorNumeric(
   palette = "viridis",
   domain = nyc_airbnb$review_scores_location)

 nyc_airbnb |> 
   filter(
     neighbourhood_group == "Manhattan",
     price < 1000) |> 
   leaflet()|> 
   addProviderTiles(providers$CartoDB.Positron) |> 
   addCircleMarkers(
     ~lat, ~long, 
     color = ~pal(review_scores_location),
     radius = 2)
```


